\documentclass{article}
\usepackage[a4paper, tmargin=1in, bmargin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{pdflscape}
\usepackage{listings}
% \usepackage{float}
%\usepackage{hyperref}
%\usepackage{titlesec}

\newcommand{\ra}{$\rightarrow$}


\begin{document}
% \maketitle

EE 344 Final Report : Visible Light Communication using LED\\
Group No. B-05\\
Faculty Incharge: Prof. Kumar Appaiah\\
TA Associated : \\
% Group Members:\\
Arka Sadhu - 140070011\\
Sudeep Salgia - 14D070011\\
Parth Kothari - 14D070019\\
% \hline

\section{Abstract}
Mark Twain had once remarked, “Buy land -- they’re not making it anymore”. Interestingly, in today’s context this holds even for the spectrum. With the spectrum limited anyway and its increased demand greatly driven by the need of the newer technologies like Internet of Things, there is an urgent need to look for solution of this spectrum-crunch. Surprisingly, the solution is staring right at us - visible light. This has led to whole new fast developing field of light fidelity or popularly known as, LiFi. It is a term often used in place of Visible Light Communication which is a technique that aims at solving the problem of illumination and communication together. It achieves this by switching the light sources at high frequencies, making it indiscernible to the human eye by measurable by a sensitive photodiode.
In our project, we aim to develop a prototype of Visible Light Based Communication link. The
project will consist of a transmitter, a LED in this case, which will transmit the message signal
which will be received by the receiver. The data transmitted would be read from a file.
\newpage
\tableofcontents

\section{Chapter 1 : Introduction}
% Give Project objective, Block diagram, Motivation for the work
\subsection{Project Objective}
The project aims at developing a prototype to establish a commununication link which uses the visible spectrum for transmission. This is popularly knowns as Visible Light Communication (VLC).  
\subsection{Block Diagram}

\subsection{Motivation for the Work}
The previous decade has seen a tremendous technological growth in the field of mobile services, Wifi and applications in the field of Internet of Things. 


\begin{itemize}
\item 
\end{itemize}
\section{Chapter 2 : Project Design}
% Give details of the system design, choice of sub systems and other design
% steps/strategy

\section{Chapter 3 : Project Implementation}
% Give details of the various subsystems (include neat circuit diagrams (no
% hand drawn diagrams please) with component values, photographs).
% Please do not give listing of your code in the report. Instead add
% comments to your code and upload it on YAWP (after the Final demo). We
% shall involve the TA/RA associated with your project for this step.
\begin{itemize}
\item Software Details
  \begin{itemize}
  \item 
  \end{itemize}
\end{itemize}
\section{Chapter 4 : Performance Evaluation}
% prototype details, test results,
% problems faced (and lessons learned), etc.
\section{Chapter 5 : Conclusion and suggestions for future work}



\end{document}

